Postural changes mediate children's visual access to faces and hands

### 2018-01-11 writeup-cogsci/cogsci2018.Rmd
figures etc.

---
title: "Developmental and postural changes in children's visual access to faces"
bibliography: xsface.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

@@

```{r, libraries}
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
```

@@

\begin{figure*}
\includegraphics[width=6in]{images/framesample.pdf}
\caption{\label{fig:frames} Sample frames from the headcam videos for a child from each age group, selected because they featured successful face detections (green squares).}
\end{figure*}

All headcam videos were cropped to exclude the period of entry to the playroom and were automatically synchronized with the tripod-mounted videos using FinalCut Pro Software. These sessions yielded a substantial amount of video: a total of
`r round(sum(inc_subs$len.min), digits = 0)` minutes (almost a milion frames), with an average video length of
`r round(sum(inc_subs$len.min)/60, digits = 2)` minutes
(min = `r round(min(inc_subs$len.min), digits = 2)`, max = `r round(max(inc_subs$len.min), digits = 2)`).

@@

# Results
We report results from three different sets of analyses. First, we explore developmental changes in posture and orientation in our dataset. Next, we explore how these changes affect access to faces and to hands, as measured using computater vision algorithms. Finally, we explore how these changes impact the accessibility of faces and hands during labeling events.

## Changes in Posture and Orientation

## Changes in Access to Faces

## Changes in Access to Hands

>>>>

---
title: "Postural changes mediate children's visual access to faces and hands"
bibliography: xsface.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

@@

```{r, libraries}
library(knitr)
knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
                      fig.path='figs/', echo=FALSE, warning = FALSE, 
                      cache=TRUE, message = FALSE, sanitize = TRUE)
library(readr)
library(plyr) # need to load this for scripts, always load before
library(dplyr)
library(tidyr)
library(xtable)
library(lubridate)
library(langcog)
library(ggplot2)
```

@@

\begin{figure*}
\includegraphics[width=6in]{images/framesample.pdf}
\caption{\label{fig:frames} Example face detections made by MTCNN for the headcam videos from a child in each group  (green squares).}
\end{figure*}

Headcam videos were trimmed such that they excluded the instruction phase when the experimenter was in the room and were automatically synchronized with the tripod-mounted videos using FinalCut Pro Software. These sessions yielded videos of 
`r round(sum(inc_subs$len.min), digits = 0)` minutes (almost a milion frames), with an average video length of
`r round(sum(inc_subs$len.min)/60, digits = 2)` minutes
(min = `r round(min(inc_subs$len.min), digits = 2)`, max = `r round(max(inc_subs$len.min), digits = 2)`).

@@

# Results
We report results from three different sets of analyses. First, we explore how these changes affect access to faces and to hands, as measured using computater vision algorithms. Second, we explore how these changes impact the accessibility of faces and hands during labeling events.

```{r}
d <- read_csv("../data/consolidated_data.csv") %>%
  mutate(posture = factor(posture), 
         orientation = factor(orientation))

facebyAge <- d %>%
  filter(!is.na(age.at.test)) %>%
  group_by(subid, age.at.test) %>%
  summarise(face = mean(face)) %>%
  left_join(inc_subs) %>%
  mutate(len = as.numeric(len_seconds/60))

faceByOrientation <- d %>%
  filter(!is.na(orientation)) %>%
  group_by(age.grp, orientation, subid) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp)

facebyPosture <- d %>%
  filter(!is.na(posture)) %>%
  group_by(age.grp, posture, subid) %>%
  summarise(face = mean(face)) %>%
  group_by(age.grp)
```

# Changes in Access to Faces

```{r fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=4, fig.height=3, fig.cap = "R plot" }
ggplot(facebyAge, aes(x = age.at.test, y = face)) + 
  geom_jitter(width = .25, aes(size = len)) + 
  geom_smooth() + 
  scale_x_continuous(breaks=c(8,12,16)) +
  scale_size_continuous(name = "Length (s)") + 
  ylab("Proportion Face Detections") + 
  xlab("Age (months)") + 
  theme_bw() 
```

```{r fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=4, fig.height=3, fig.cap = "R plot" }
ggplot(facebyPosture, aes(x = factor(age.grp), y = face, col = posture)) + 
  geom_boxplot() + 
  ylab("Proportion Face Detections") + 
  xlab("Age (months)") + 
  theme_bw()
```

```{r fig.env="figure", fig.pos = "H", fig.align = "center", fig.width=4, fig.height=3, fig.cap = "R plot" }
ggplot(faceByOrientation, aes(x = factor(age.grp), y = face, col = orientation)) + 
  geom_boxplot() + 
  ylab("Proportion Face Detections") + 
  xlab("Age (months)") + 
  theme_bw() 
```

# Changes in Access to Hands
